TODO LIST

### 2019-03-01 LMCS/sendrev/response-letter.tex

	\setlength\itemsep{0.5em}
%	\item[$\checkmark$] running title is ``COUNTING''
%	\item on definition of functions, \verb|\colon| should be used instead of :
	\item In \cite{DBLP:conf/csl/0001HKV16}, a similar hierarchy to the one by Saluja et al. was introduced and studied. This work should be cited.

@@

\end{itemize}

\bigskip

\section*{Reviewer 2}

\begin{itemize}
	\setlength\itemsep{0.5em}
	\item \red{In several proofs, you rely on disjoint union of solutions and cartesian product of solutions. Indeed, its gives a polynomial time counting reduction. Can you make connections with (+,*) circuits ? It would be similar to what is done in A Circuit-Based Approach to Efficient Enumeration (Antoine Amarilli, Pierre Bourhis, Louis Jachiet, Stefan Mengel) where simple circuits (dDNNF, which are basically disjoint unions and cartesian products) are used to capture the solutions of MSO queries. In general I would be interested to know the relationship of your couting classes with their enumeration counterpart. 
	For instance there is a paper adapting [39] to enumeration: Enumeration Complexity of Logical Query Problems with Second-order Variables (Arnaud Durand and Yann Strozecki). In particular they consider class with some Horn structure to capture easy enumeration problems, it may have some connection with the class $\sigma$ QSO($\Pi_1$ Horn) you introduce.}

	We thank the reviewer for showing us the literature regarding enumeration problems, in particular, for the paper from Durand and Strozecki. Unfortunately, the relation between our framework with enumeration complexity classes goes beyond the scope of the paper. Nevertheless, in the last section we added a final paragraph pointing out this connection as an interesting open question.

	\item \red{For the most involved proofs, you could describe informally your proof strategy in a few lines to help the reader. You may also add some example to illustrate the different fragment of QSO (you already do it sometimes and it is very helpful).}

	Although we agree that adding more proof sketches and examples would help, the paper is already too long for adding more additional content. Furthermore, as the reviewer mentioned we already have this for the main definitions and proofs (e.g. proof of substraction by 1 at Theorem 5.9). For this reason, we decided to keep the paper as it is in terms of more examples and proof sketches.

%	\item[$\checkmark$] page 4: -some of the $\to$ some of them 
%	\item[$\checkmark$] page 10:  -$2^{|A|^l}$-bits $\to$ $2^{|A|^l}$ bits
%	\item[$\checkmark$] page 21: -it does not mentioned $\to$ it does not mention
%	\item page 22: -you make a long proof about some closure under subtraction by one. You should put the result in a theorem envirpnment to make what you are proving more evident.
%	\item[$\checkmark$] -replace .... for $\to$ replace ... by;  there are several instances of that
%	\item[$\checkmark$] -$\phi$ is an FO-formula $\to$ a $\Sigma_1[FO]$ formula
%	\item -you explain that you rewrite your formula to obtain conditions a,b and c, you should give an idea how these conditions will be used
%	\item[$\checkmark$] page 23: a SO, a FO  an SO, an FO
%	\item page 24: 	if, if $\phi$$\to$ $\phi$
	\item \red{page 25: 	-you explain that the proof relies on witnesses of logarithmic size.	It was not clear to me while reading the proof. Can you explain more ?}

	This is discussed in the response to Reviewer 1.

	\item \red{page 28:	The complete problem for $\Sigma\text{QSO}(\Sigma_2\text{-Horn})$ would be complete also for $\#(\Sigma_2\text{-Horn})$. You should mention here that you do not need sum here and that the framework of [39] is enough for this result.}

	Indeed, from the proof of Theorem 5.14 one can also derive that $\#(\Sigma_2\text{-Horn})$ is equivalent to $\Sigma\text{QSO}(\Sigma_2\text{-Horn})$ and, thus, the framework of [39] is enough for defining this class of problems. At the end of Section 5, we added a paragraph mentioning this.

%	\item[?] page 30: ``this notion can be used to captures FP'' $\to$ ``... to capture FP''
%	\item[$\checkmark$] page 32: - paths of length at most n $\to$ in an acylic graph, all paths are of size less than n
%	\item page 33: 	-there is a proof symbol \verb|\qed| but it does not end a well defined proof environment
	\item \red{page 38: the last sentence on fixed point operator is to vague. Either expand it to say what king of question on fixed point operator you want to investigate or remove it.}

	We agree with the reviewer and we decided to remove this sentence. 
\end{itemize}

\bibliographystyle{plain}
\bibliography{0001HKV16}

### 2019-03-01 LMCS/sendrev/todo-list.tex
Revisión de Reviewer 2.

\usepackage{fullpage}
\usepackage{cite}
\usepackage{amsmath,amsfonts,amssymb,mathabx}
\usepackage{stmaryrd}
\usepackage[textwidth=2cm,textsize=small]{todonotes}
\usepackage{enumitem}
\input{macrosplain}

@@

\item[$\checkmark$] p.33: ``executes exactly $n^k$ steps for a fixed $k \geq 1$'' → ``executes exactly $n^k$

@@

\begin{itemize}
		\setlength\itemsep{0.5em}
\item In several proofs, you rely on disjoint union of solutions and cartesian product of solutions. Indeed, its gives a polynomial time counting reduction. Can you make connections with (+,*) circuits ? It would be similar to what is done in A Circuit-Based Approach to Efficient Enumeration (Antoine Amarilli, Pierre Bourhis, Louis Jachiet, Stefan Mengel) where simple circuits (dDNNF, which are basically disjoint unions and cartesian products) are used to capture the solutions of MSO queries.

\item In general I would be interested to know the relationship of your couting classes with their enumeration counterpart. 
For instance there is a paper adapting [39] to enumeration: Enumeration Complexity of Logical Query Problems with Second-order Variables (Arnaud Durand and Yann Strozecki). In particular they consider class with some Horn structure to capture easy enumeration problems, it may have some connection with the class $\sigma$ QSO($\Pi_1$ Horn) you introduce.

\item For the most involved proofs, you could describe informally your proof strategy in a few lines to help the reader. You may also add some example to illustrate the different fragment of QSO (you already do it sometimes and it is very helpful).
\martin{me gustar\'ia que conversemos qu\'e demostraciones necesitan esto, y si el outline de la demostraci\'on de -1 basta. Tambi\'en qu\'e fragmentos de QSO necesitan un ejemplo.}

\item[$\checkmark$] page 4:
-some of the $\to$ some of them 
\item[$\checkmark$] page 10: 
-$2^{|A|^l}$-bits $\to$ $2^{|A|^l}$ bits
\item[$\checkmark$] page 21:
-it does not mentioned $\to$ it does not mention
\item[$\checkmark$] page 22: 
-you make a long proof about some closure under subtraction by one.
You should put the result in a theorem envirpnment to make what you are
proving more evident.
\item[$\checkmark$] -replace .... for $\to$ replace ... by;  there are several instances of
that
\item[$\checkmark$] -$\phi$ is an FO-formula $\to$ a $\Sigma_1[FO]$ formula
\item[$\checkmark$] -you explain that you rewrite your formula to obtain conditions a,b and c, 
you should give an idea how these conditions will be used
\item[$\checkmark$] page 23:
a SO, a FO  an SO, an FO
\item[$\checkmark$] page 24: 
if, if $\phi$$\to$ $\phi$
\item page 25: 
-you explain that the proof relies on witnesses of logarithmic size.
It was not clear to me while reading the proof. Can you explain more ?
\martin{no logr\'e corregir esto, es la misma acotaci\'on que el Reviewer 1}
\item page 28:
-the complete problem for $\Sigma$ QSO($\Sigma_2$ Horn) would be complete also for $\#\Sigma-2$ Horn. You should mention here that you do not need sum here
and that the framework of [39] is enough for this result.
\martin{conversemos esto}
\item[$\checkmark$] page 30: ``this notion can be used to captures FP'' $\to$ ``... to capture FP''

@@

\item page 38: 
the last sentence on fixed point operator is to vague. Either expand it to 
say what king of question on fixed point operator you want to investigate or remove it	
\martin{conversemos esto}
\end{itemize}

>>>>

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{fullpage}
\usepackage{cite}
\usepackage{amsmath,amsfonts,amssymb,mathabx}
\usepackage{stmaryrd}
\usepackage[textwidth=2cm,textsize=small]{todonotes}
\usepackage{enumitem}
\input{macrosplain}

@@

\item[$\checkmark$] p.33: ``executes exactly $n^k$ steps for a fixed $k \geq 1$'' $\rightarrow$ ``executes exactly $n^k$

@@

\begin{itemize}
		\setlength\itemsep{0.5em}
\item[$\checkmark$] In several proofs, you rely on disjoint union of solutions and cartesian product of solutions. Indeed, its gives a polynomial time counting reduction. Can you make connections with (+,*) circuits ? It would be similar to what is done in A Circuit-Based Approach to Efficient Enumeration (Antoine Amarilli, Pierre Bourhis, Louis Jachiet, Stefan Mengel) where simple circuits (dDNNF, which are basically disjoint unions and cartesian products) are used to capture the solutions of MSO queries.

\item[$\checkmark$] In general I would be interested to know the relationship of your couting classes with their enumeration counterpart. 
For instance there is a paper adapting [39] to enumeration: Enumeration Complexity of Logical Query Problems with Second-order Variables (Arnaud Durand and Yann Strozecki). In particular they consider class with some Horn structure to capture easy enumeration problems, it may have some connection with the class $\sigma$ QSO($\Pi_1$ Horn) you introduce.

\cristian{No tiene mucho sentido estos comentarios del reviewer ya que va más alla del paper. Para dejarlo tranquilo, agregue un último comentario en las conclusiones diciendo que sería interesante estudiar estos problemas en el contexto de enumeración. También agregue la respuesta a la carta.}

\item[$\checkmark$] For the most involved proofs, you could describe informally your proof strategy in a few lines to help the reader. You may also add some example to illustrate the different fragment of QSO (you already do it sometimes and it is very helpful).
\martin{me gustar\'ia que conversemos qu\'e demostraciones necesitan esto, y si el outline de la demostraci\'on de -1 basta. Tambi\'en qu\'e fragmentos de QSO necesitan un ejemplo.}

\cristian{El paper ya tiene demasiados ejemplos y ya esta demasiado largo. En la carta le respondí que lamentablemente, debido a que el paper esta demasiado largo, decidimos no agregar mas ejemplos.}

\item[$\checkmark$] page 4:
-some of the $\to$ some of them 
\item[$\checkmark$] page 10: 
-$2^{|A|^l}$-bits $\to$ $2^{|A|^l}$ bits
\item[$\checkmark$] page 21:
-it does not mentioned $\to$ it does not mention
\item[$\checkmark$] page 22: 
-you make a long proof about some closure under subtraction by one.
You should put the result in a theorem envirpnment to make what you are
proving more evident.
\item[$\checkmark$] -replace .... for $\to$ replace ... by;  there are several instances of
that
\item[$\checkmark$] -$\phi$ is an FO-formula $\to$ a $\Sigma_1[FO]$ formula
\item[$\checkmark$] -you explain that you rewrite your formula to obtain conditions a,b and c, 
you should give an idea how these conditions will be used
\item[$\checkmark$] page 23:
a SO, a FO  an SO, an FO
\item[$\checkmark$] page 24: 
if, if $\phi$$\to$ $\phi$
\item[$\checkmark$] page 25: 
-you explain that the proof relies on witnesses of logarithmic size.
It was not clear to me while reading the proof. Can you explain more ?
\martin{no logr\'e corregir esto, es la misma acotaci\'on que el Reviewer 1}
\cristian{Le respondí diciendo que es mencionado en la respuesta al otro reviewer.}
\item[$\checkmark$] page 28:
-the complete problem for $\Sigma$ QSO($\Sigma_2$ Horn) would be complete also for $\#\Sigma-2$ Horn. You should mention here that you do not need sum here
and that the framework of [39] is enough for this result.
\martin{conversemos esto}
\cristian{Agregue un parrafo al final de la sección 5 mencionando esto. De hecho, desde la demostración uno puede demostrar que las dos classes son iguales (la suma de afuera no te agrega expresividad). Le respondí esto mismo en la carta.}
\item[$\checkmark$] page 30: ``this notion can be used to captures FP'' $\to$ ``... to capture FP''

@@

\item[$\checkmark$] page 38: 
the last sentence on fixed point operator is to vague. Either expand it to 
say what king of question on fixed point operator you want to investigate or remove it	
\martin{conversemos esto}
\cristian{Tiene razón y eliminé esta oración al final del paper.}
\end{itemize}
